Sex-Based Differences in Tuberculosis Immune Response: The Role of Leptin

### 2025-03-14 products/manuscript/Manuscript.qmd
Main analysis - 1

*This part is under construction:* I will firstly compare body indices and immune response measures between males and females. To measure leptin’s effect in modulating immune activation and to link body energy storage with immune response strength, my initial plan is to use regression analysis to examine leptin’s mediator effect, but I’m seeking a more appropriate method. Of note, the sample size is relatively small, which may influence the significance of hypothesis tests.

@@

```{r}
#| label: tbl-body
#| tab-cap: "Body characteristics and composition by sex."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table1.png"))
```

@@

>>>>

@@

```{r}
#| label: tbl-body
#| tbl-cap: "Body characteristics and composition by sex."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table1.png"))
```

@@

(@tbl-coef)

```{r}
#| label: tbl-coef
#| tbl-cap: "Coefficient estimation (95% CI) from linear regression and Poisson regression."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table2.png"))
```

(@tbl-ma)

```{r}
#| label: tbl-ma
#| tbl-cap: "Mediation analysis with estimated effects and 95% CI."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table3.png"))
```
